A survey of HTTP caching options on the open Web

### 2015-01-04 sanity/paper1.tex
some additional todos
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@931 43ef1190-90fd-4dd7-a769-d0121f02b80e
writeup about servers
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@932 43ef1190-90fd-4dd7-a769-d0121f02b80e

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\httph}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

@@

@@

>>>>

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\pvalue}{\textit{p}-value}
\newcommand{\httph}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

@@

Key contributions of this paper are:\todo{write}

@@

\section{Analytics}

\subsection{Different server implementations}

First, we investigated whether certain servers provided better support
for caching than others. To do this, we formulated SPARQL queries to
examine the \httph{Server} headers of successful responses, with
optional clauses matching the standard-compliant computed freshness
time (which is the ideal) as well as whether the response had other
promising features that could assist caching, such as \httph{ETag}s,
modification time, certain predicates, etc.

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising feature. For
the former, this amounted to 22 servers, tabulated in~\todo{include
  table}. 70 servers always responded with promising features. As we
can see, apart from well-known Virtuoso and Callimachus servers, as
well as the Perl modules RDF::LinkedData and RDF::Endpoint, which is
partly developed by and runs on a server operated by this author, most
headers tells very little about the RDF-specific parts of the
underlying server implementation.

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others. To
test this hypothesis, we create two so-called \emph{contigency
  tables}\todo{ref}. This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is only to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.

Using the statistics system R\todo{ref}, we use a statistical test,
namely Pearson's $\chi^2$ test with simulated \pvalue (based on 10000
replicates). The simulation is done using a Monte Carlo method to
compensate for the fact that many servers will not expose caching
headers at all.

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only report generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints. \todo{do this specifically
  for SPARQLES endpoints?}

\section{Recommendations}\todo{write}
